Reply to reviewers concerning submission sensors-238686: "An efficient audio coding scheme for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach"

### 2017-11-16 paper/articleV2.tex
paper revision

The identification of sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental data in which the current work falls. Studied classification methods are diverse, ranging from time-dependant modeling with hidden Markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}. Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}. Also, several type of features are considered to feed those classifiers. The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal. Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most widely used as of today. These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale. Features can also be computed in other domains to better model signal properties. For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features. Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a clustering technique. Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}. A more detailed review of used methods is available in \cite{chachada2013}.

@@

\begin{figure*}[htbp]
	\centering
		\includegraphics[width=.9\textwidth]{figures/scheme.pdf}
	\caption{Overview of the coder process.}
	\label{fig:scheme}
\end{figure*}

@@

\subsection{Event recognition} \label{sec:event_p}

@@

\begin{figure*}[htbp]
	\centering
		\includegraphics[width=.9\textwidth]{figures/class.pdf}
	\caption{Classification process flowchart. Here third-octave bands are obtained by reversing the operations in Section~\ref{sec:dataenc}. Cepstral coefficients are then computed before training the model. Cross-validation is achieved by independantly training and testing the models with each of the 10 combination of a 90\%-10\% training-validation dataset separation. Accuracy results are considered only for validation (not encountered during training) data.}
	\label{fig:class_flwc}
\end{figure*}

@@

This test requires an implementation of the inverse operation of the coding process to provide the listener with an estimate of the time-domain signal. To do so, a linearly-scaled spectrogram from the band-focused representations is estimated. This estimation is achieved by multiplying the spectral representation by the scaled transpose of the forward transformation matrix. A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}. The signal phase is recovered with the Griffin \& Lim algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not. The time-domain signal is then retrieved using the overlap-add method. When using overlap to compute third-octave bands, framing effects produced by rectangular windowing are reduced by convoluting the signal with a Hann windowing function prior to inverse-STFT computation.

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.5\textwidth]{figures/freq.png}
	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location. This process yields an important and heterogeneous loss in resolution, particularly at higher frequency points.}
	\label{fig:freq}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.5\textwidth]{figures/class_mel_q.eps}
	\caption{Classification accuracy as a function of word size before encoding. The baseline plotted on the right is computed without quantizing the representation.}
	\label{fig:class_mel_q}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.5\textwidth]{figures/class_tob_q.eps}
	\caption{Classification accuracy with third-octave bands and varying word size.}
	\label{fig:class_tob_q}
\end{figure}

>>>>

The identification of sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental data in which the current work falls. Studied classification methods are diverse, ranging from time-dependant modeling with hidden Markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}. Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}. Also, several type of features are considered to feed those classifiers. The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal. Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most widely used as of today. These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale. Features can also be computed in other domains to better model signal properties. For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features. Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}. Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a clustering technique. More complex systems using multiple-domain data representation as well as unsupervised models have been found to handle unrestricted environments suche as urban acoustic scenes efficiently \citep{ntalampiras2012}. A more detailed review of used methods is available in \cite{chachada2013}.

@@

\begin{figure*}[htbp]
	\centering
		\includegraphics[width=.9\textwidth]{figures/scheme.pdf}
	\caption{Overview of the encoding process.}
	\label{fig:scheme}
\end{figure*}

@@

\subsection{Preserving event recognition performance at low bitrate} \label{sec:event_p}

@@

\begin{figure*}[t]
	\centering
		\includegraphics[width=.9\textwidth]{figures/class.pdf}
	\caption{Classification process flowchart. Here third-octave bands are obtained by reversing the operations in Section~\ref{sec:dataenc} and cepstral coefficients are computed before training the model. Cross-validation is achieved by independantly training and testing the models with each of the 10 combination of a 90\%-10\% training-validation dataset separation.}
	\label{fig:class_flwc}
\end{figure*}

@@

This test requires an implementation of the inverse operation of the coding process to provide the listener with an estimate of the time-domain signal. To do so, a linearly-scaled spectrogram from the band-focused representations is estimated. This estimation is achieved by multiplying the spectral representation by the scaled transpose of the forward transformation matrix. A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}. In fact, each white square can be interpreted as the filter applied to obtain a single third-octave band. The filtering process will average the energy content of the signal over the corresponding band. As a result the energy located at a specific frequency is impossible to recover and the best inverse approximation is to split the third-octave band's observed energy into all the corresponding frequency bins with the same proportions as during analysis. This leads to the phenomenon seen on Figure~\ref{fig:freq} where part of the energy of a frequency bin in the original signal is found in all other bins of the same band at reconstruction, in almost equal proportions. The signal phase is recovered with the Griffin \& Lim algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not. The time-domain signal is then retrieved using the overlap-add method. When using overlap to compute third-octave bands, framing effects produced by rectangular windowing are reduced by convoluting the signal with a Hann windowing function prior to inverse-STFT computation.

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.5\textwidth]{figures/freq.png}
	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location. Here a brighter gray indicates that part of the energy contained at the corresponding frequency of the original signal is transferred to the reconstructed signal at the indicated frequency. This process yields an important and heterogeneous loss in resolution, particularly at higher frequency points.}
	\label{fig:freq}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.8\textwidth]{figures/class_mel_q.eps}
	\caption{Classification accuracy as a function of word size before encoding. The baseline plotted on the right is computed without quantizing the representation.}
	\label{fig:class_mel_q}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.8\textwidth]{figures/class_tob_q.eps}
	\caption{Classification accuracy with third-octave bands and varying word size.}
	\label{fig:class_tob_q}
\end{figure}

### 2017-11-16 paper/sensors/coverLetter.tex
paper revision

@@

$\rightarrow$ While a single audio channel was selected for this study, a multiple channel encoding can be performed by applying the Delta compression along both the time and channels dimensions. As the transmitted data primarily consists of energetic measurements, additional channels are likely to be encoded very efficiently due to the redundancy of information already contained in the first channel.

FELIX : reference to where the article has been modified.

@@

$\rightarrow$ This would be a very interesting avenue of research that could be considered for future work.

FELIX give ref to where you discuss this the paper.

>>>>

CATHERINE: Est-il possible de dédier un petit paragraphe à la question dans la conclusion?

@@

$\rightarrow$ While a single audio channel was selected for this study, a multiple channel encoding can be performed by applying the Delta compression along both the time and channels dimensions. As the transmitted data primarily consists of energetic measurements, additional channels are likely to be encoded very efficiently due to the redundancy of information already contained in the first channel. Future work using this idea in a sensor grid is now discussed in the conclusion.

@@

$\rightarrow$ This would be a very interesting avenue of research that could be considered for future work. The discussion on data representations and models used in environmental audio event recognition (Section 2.1) has been extended to include related works.
